### 2023-06-05 README.Rmd
new try ... 230605

<ul>
<li>
`createHOT`: creates the validation/holdout task for you. For example, in a *CBC* the total utilities are calculated by the sum of each attribute level. You have to specify the attribute levels for each alternative in the validation/holdout task and it will calculate the total utility for each alternative in the validation/holdout task.
</li>
<li>
`accuracy`: generates the number of correct predicted choice or no-choice divided by the total number of predictions. Only possible for a binary output, e.g., buy vs. no-buy correctly predicted.
</li>
<li>
`f1`: generates the F1-Score. F1-Score is calculated by the following formula $\frac{2 * precision * recall}{precision + recall}$. Only possible for a binary output, e.g., buy vs. no-buy correctly predicted.
</li>
<li>
`f1`: generates the F1-Score. F1-Score is calculated by the following formula $\frac{2 * precision * recall}{precision + recall}$. Only possible for a binary output, e.g., buy vs. no-buy correctly predicted.
</li>

>>>>

<ul>
<li>
<code>createHOT</code>: creates the validation/holdout task for you. For example, in a *CBC* the total utilities are calculated by the sum of each attribute level. You have to specify the attribute levels for each alternative in the validation/holdout task and it will calculate the total utility for each alternative in the validation/holdout task.
</li>
<li>
<code>accuracy</code>: generates the number of correct predicted choice or no-choice divided by the total number of predictions. Only possible for a binary output, e.g., buy vs. no-buy correctly predicted.
</li>
<li>
<code>f1</code>: generates the F1-Score. F1-Score is calculated by the following formula $\frac{2 * precision * recall}{precision + recall}$. Only possible for a binary output, e.g., buy vs. no-buy correctly predicted.
</li>
</ul>
